Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-27 WSSSPE1_report/WSSSPE1_summary_report.tex
reorder/fix some names, hopefully not messing anything up in the process
small fixes
resolving a couple of notes, adding a new one

The question of whether funders, such as the NSF, can mandate software plans in
much the same way as they do data management plans, was raised. Daniel Katz responded that
software is supposed to be described as part of the NSF data management plan,
and that in their \note{who is ``they''? OCI? NSF?} definition, data includes software. A comment from Twitter
(@biomickwatson) raised the issue that this requires reviewers and funders who
understand the answers that are given in these plans. Daniel Katz responded
that in programs focused on software or data this can be done effectively, but
agreed that in more general programs this is indeed a problem.

@@

\note{So far this reads a lot like a collection of thoughts only, without ``red line''.}
The question of what was meant by ``sustainability'' in the context of software
came up in many different parts of the workshop, specifically in the first
keynote (\S\ref{sec:keynote1}), the Developing and Maintaining Software panel,
and the Policy panel.

@@

\note{We should use either single or double quotations consistently throughout the paper.}
For the purpose of studying software case studies, we classify the software
projects discussed in the workshop in three broad categories. The first is 
`utility software', software tools that enable and/or facilitate the
development of other tools and techniques to carry out scientific work. The second is
`scientific software', software that was developed with an aim to solve a
class of scientific problems. The third is `infrastructure software', software
developed to efficiently utilize new research infrastructure.

@@

Lorena A Barba

@@

Neil Chue Hong

@@

AllisonGehrke

@@

Monica Luecke

@@

Eric Van Wyk

>>>>

The question of whether funders, such as the NSF, can mandate software plans in
much the same way as they do data management plans, was raised. Daniel Katz responded that
software is supposed to be described as part of the NSF data management plan,
and that in NSF's definition, data includes software. A comment from Twitter
(@biomickwatson) raised the issue that this requires reviewers and funders who
understand the answers that are given in these plans. Daniel Katz responded
that in programs focused on software or data this can be done effectively, but
agreed that in more general programs this is indeed a problem.

@@

\note{So far this reads a lot like a collection of thoughts only, without ``red line''.}
\note{Dan: assuming the previous note is from FL, what do you propose?}
The question of what was meant by ``sustainability'' in the context of software
came up in many different parts of the workshop, specifically in the first
keynote (\S\ref{sec:keynote1}), the Developing and Maintaining Software panel,
and the Policy panel.

@@

For the purpose of studying software case studies, we classify the software
projects discussed in the workshop in three broad categories. The first is 
utility software, software tools that enable and/or facilitate the
development of other tools and techniques to carry out scientific work. The second is
scientific software, software that was developed with an aim to solve a
class of scientific problems. The third is infrastructure software, software
developed to efficiently utilize new research infrastructure.

@@

Lorena A. Barba

@@

Neil Chue Hong %surname is Chue Hong, this is the correct order.

@@

Allison Gehrke

@@

Monica L\"{u}cke

@@

Eric van Wyk
